Concurrent Programming with CXL

### 2020-06-20 book/paper.tex
Added more exercises

\section*{Exercises}
\begin{enumerate}
\item Assume that you have only binary semaphores.  Implement counting
semaphores using binary semaphores.
\end{enumerate}

@@

\begin{quote}
\begin{itemize}
\item Implement the producer/consumer problem with SBS.
\end{itemize}
\end{quote}

>>>>

@@

\section*{Exercises}
\begin{enumerate}
\item Assume that you have only binary semaphores.  Implement counting
semaphores using binary semaphores using split binary semaphores.
\item Implement a solution to the producer/consumer problem
(Figure~\ref{fig:boundedbuffer}) using split binary semaphores.
\end{enumerate}
